The globular cluster system of the Auriga simulations

### 2019-07-11 AurigaGCS.tex
Attempt to motivate each figure, and  explain their take away message for Sec. 4.3

>>>>

We notice in Figure~\ref{fig:Au-FeHRgc} that the Auriga simulations, on average,
produce fewer GCs in the lowest metallicity bins ($-2.5$ to $-1.5$) than at higher 
metallicities in the three innermost radial bins. In addition, Auriga produces 
fewer high-metallicity GCs at large radii, similar to the MW and M31 GC systems. 
However, the three bins in the upper right corner are populated in the Auriga
simulations, in contrast to the observations. The top panel of 
Figure~\ref{fig:Au-FeHRgc-ratio} shows that the mass excess for Auriga GCs within
the Solar radius decreases with decreasing metallicity. This means that either
the formation efficiency should increase with decreasing metallicity, or that 
the lowest-metallicity GCs in the Auriga simulations are less strongly affected
by disruptive processes, if the star formation histories in the Auriga simulations
are to give rise to a GC system that can be similar to the GCS that is observed
in the Milky Way. Moreover, either a lower formation efficiency is required at
large radii, or stronger disruption. Disruption of star clusters is expected to
be more efficient at smaller radii due to higher tidal forces in the innermost
region for GCs on orbits that pass through the disk, or with pericenters close 
to the bar or bulge. Compared to Andromeda, the mass excess (bottom panel of 
Figure~\ref{fig:Au-FeHRgc-ratio}) shows a less clear trent than for the Milky Way. 
Most bins show mass surplus factors of few tens, meaning that high formation 
efficiencies would be required in addition to little disruption for the Auriga 
simulations to yield a GC system consistent with that of the Andromeda galaxy.
